Missing The Point

### 2020-09-11 Manuscript.Rmd
Simplified simulation

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

@@

```{r echo=FALSE}
load("~/MissingThePoint/Data/results.Rdata")
results %>% 
  ggplot() + 
  geom_hline(yintercept = 0.3334) +
  geom_point(aes(x=it, y=est, color = mech, shape = as.factor(p))) + 
  geom_line(aes(x=it, y=est, color = mech, linetype = as.factor(p))) + 
  theme_classic()
```
